Matching bullets

### 2015-11-15 imaging-paper.Rnw
Sketch the later sections
Start some discussion of the land images

>>>>

% Methodology
Throughout this section, we will work with images from the James Hamby Consecutively Rifled Ruger Barrel Study. Ten Ruger P-85 pistol barrels were obtained from the manufacturer and fired to produce known test bullets and unknown bullets for comparison. 3D topographical images are provided in format called x3p. The x3p format was developed as a means for forensic examiners to easily exchange images in a standard format. It was adopted by the OpenFMC (Open Forensic Metrology Consortium), a group of academic, industry, and government Firearm Forensics researchers whose aim is to establish best practices for researchers using metrology in the forensic sciences.

Each fired bullet is provided as a set of six x3p files, where each file is a surface scan between two bullet grooves, called a ``land". An example of plotting one of these lands is given in Figures \ref{fig:sidex3p} and \ref{fig:topx3p}, which show side and top profiles of the land respectively.

\begin{figure}
  \centering
    \includegraphics[width=\linewidth]{images/sidex3p.png}
  \caption{An example of a scan of a bullet land, viewed from the side.}
  \label{fig:sidex3p}
\end{figure}

\begin{figure}
  \centering
    \includegraphics[width=\linewidth]{images/topx3p.png}
  \caption{An example of a scan of a bullet land, viewed from the top.}
  \label{fig:topx3p}
\end{figure}

% Application

% Conclusion
